## Meta-analysis methodology

What is it?

### from doing meta-analysis

LOOK AT:

-   

-   Borenstein, Michael, Larry V Hedges, Julian PT Higgins, and Hannah R Rothstein. 2011. *Introduction to Meta-Analysis*. John Wiley & Sons. chapter 40

-   https://absolutelymaybe.plos.org/2017/07/03/5-tips-for-understanding-data-in-meta-analyses/

-   https://statistically-funny.blogspot.com/2012/10/a-dip-in-data-pool.html

### Effect size

-   Typically:

-   using overall accuracy as an effect size

    -   proportion

    -   what are the implications of that

    -   what is this true effect I am looking to model

    -   overall effect?

ways to calculate overall effect: DerSimonion--Laird random effects estimator

"Previous research suggest that between-study variation could cause bias (Borenstein 2019). To control for this factor, we estimated three indicators of study heterogeneity: Cochran's Q, I 2, and τ . While Cochran's Q is sensitive to the number of studies and the study size, Higgins and Thompson (2002) suggested to also report I 2, which is not sensitive to the number of studies but to the study size. By contrast, τ is neither sensitive to the number of studies included nor to the study size (Schwarzer, Carpenter, and Rücker 2015)."

confused about how the first sentence leads to the next one

# Analysis plan

1.  check for between study heterogeneity in the "standard" method assuming that results are independent and not from the same study.
2.  aggregate the results per study (2.1 mean, 2.2. median) check again
3.  Instead of using SE set to 1
4.  multilevel
    1.  3-level: papers are not independent
    2.  look if you can have more levels

Look at how different methods 1-4 are

Look for outliers/ influenial cases: GOSH plots

Meta-regression

# Results

### Data

```{r}
library(tidyverse)
library(readxl)
extracted_features <- read_excel("extracted_features.xlsx", sheet = "Include",  na = "NA")

citations<- read.csv("appendix/app1-paper_selection/citations.csv")

citations$AutherYear <- paste(strsplit(citations$Author, "[,]")[[1]][1], "et al,", citations$Publication.Year) 

citations_needed<- subset(citations, DOI %in% extracted_features$DOI, 
                          select = c(DOI, AutherYear, Publication.Title))


strsplit(citations$Author, "[,]")[[1]][1]
sub("\\|.*", "", citations$Author)
dat <- inner_join(citations_needed, extracted_features, by = "DOI")

length(unique(dat$DOI))


```

## Descriptives

plots with locations, table of variable distributions etc

```{r}

```

```{r}
ggplot(sample, aes(x = OA_reported))+
  geom_histogram()
ggplot(sample, aes(x = log(OA_reported/(1-OA_reported))))+
  geom_histogram()
```

```{r}
ggplot(sample, aes(x = log(RS_spectral_bands_no), y = log(OA_reported/(1-OA_reported)), 
                colour = model_group
                ))+
  geom_point()
```

Data with totals

```{r}
sum(is.na(sample$'totals(objects_area_validationpoints_pixels)'))
data <- sample|> drop_na('totals(objects_area_validationpoints_pixels)')


```

## Meta-analysis 1: assuming independence

ignoring with in study dependence

```{r}
library(meta)

data1 <- rowid_to_column(sample, "ID") 


m.prop <- metaprop(event = `confusion_matrix diagonal`,
                   n = total,
                   studlab = file_name,
                   data = sample_with_n,
                   method = "GLMM",
                   sm = "PLOGIT",
                  method.random.ci = "HK",
                   fixed = TRUE,
                   random = TRUE,
                   title = "Overall Accuracy")
summary(m.prop)
```

### a. Typical calculation of SE

### b. SE = 1

### c. Comparison of the methods

## Meta-analysis 2:
