# Results

X articles were included with Y model records for meta-analysis extracted. Most studies were from countries

::: {#tbl-extracted_features}
| Feature                 | Definition                                                                                    | value/categories                                                                                 |
|-----------------|---------------------------|----------------------------|
| Paper ID                | DOI used as identification number of the article                                              |                                                                                                  |
| Author(s), year, DOI    | Name(s) of authers                                                                            |                                                                                                  |
| Title                   | Title of the article                                                                          |                                                                                                  |
| Year                    | Publication Year                                                                              |                                                                                                  |
| Publication name        | Name of journal that published paper                                                          |                                                                                                  |
| Location                | Location of the data used (country level)                                                     |                                                                                                  |
| Research Theme          | Area of research                                                                              | TO DO: Add categories                                                                            |
| RS device               | Type of RS device                                                                             | Satellite , Drone, Plane, Unmanned Aerial Vehicles (UAVs)                                        |
| RS device specifics     | Specific device name                                                                          | Sentinel-2, Landsat-8                                                                            |
| RS device               | Grouping?                                                                                     |                                                                                                  |
| Ancillary data          | Use of non-RS data in the model                                                               | {0 = only remote sensed data, 1= additional data used} Additional (non- remote sensed data used) |
| Training/Test set       | Some confusion here if the test set or training set used, maybe I will add this as a feature! | test, train, not specified, ....                                                                 |
| RS bands                | list of the bands used                                                                        |                                                                                                  |
| RS_spectral_bands_no    | number of bands used                                                                          |                                                                                                  |
| RS_spatital_resolution  | in meters                                                                                     |                                                                                                  |
| model_group             | Algorithm group used                                                                          | Random forest (RF), artificial neural network (ANN), support vector machine (SVM),               |
| number_classes          | The number of classes to predict                                                              |                                                                                                  |
| fraction_majority_class | The fraction of the largest class                                                             |                                                                                                  |
| Total                   | Sample size                                                                                   |                                                                                                  |
| Accuracy metric         | Measure used to assess the predictive performance of the ML method applied                    | Overall Accuracy (OA)                                                                            |

: A listing of extracted features considered for the content analysis of included articles
:::

### Descriptive stats

```{r}
library(tidyverse)
library(readxl)
extracted_features <- read_excel("extracted_features.xlsx", sheet = "Include",  na = "NA")


citations<- read.csv("appendix/app1-paper_selection/citations.csv")


citations$AuthorYear <- paste(sapply(strsplit(citations$Author, ", "), 
                                     `[`, 1), "et al.", 
                              citations$Publication.Year)

citations_needed<- subset(citations, DOI %in% extracted_features$DOI, 
                          select = c(DOI, AuthorYear, Publication.Title, Publication.Year))

dat <- inner_join(citations_needed, extracted_features, by = "DOI")


```

Overal dataset Distribution of papers over:

-   time

    ```{r}
    ggplot(citations)+
      geom_histogram(mapping = aes(x=Publication.Year), bins = 30)
    ```

#### Randomly Selected Studies

-   which algorithms performed better (look if pairwise comparison is possible

-   countries

```{r}
dat %>%
  group_by(AuthorYear, location) %>%
  summarise(counts = n())
```

-   journals

-   does OA increase with publication date

```{r}
ggplot(dat, mapping = aes(x =Publication.Year, y = OA_reported, colour = AuthorYear))+
  geom_point() +
  geom_smooth(formula = 'y ~ x', method = "lm", se = FALSE, color = "black") 

```

```{r}
mean_data <- dat %>%
  group_by(Publication.Year, AuthorYear) %>%
  summarise(
    mean_OA_reported = mean(OA_reported, na.rm = TRUE),
    min_OA_reported = min(OA_reported, na.rm = TRUE),
    max_OA_reported = max(OA_reported, na.rm = TRUE)
  )


ggplot(mean_data, aes(x = Publication.Year, y = mean_OA_reported, colour = AuthorYear)) +
  geom_point() +
  geom_errorbar(aes(ymin = min_OA_reported, ymax = max_OA_reported), width = 0.2) +
  geom_smooth(formula = 'y ~ x', method = "lm", se = FALSE, color = "black") + 
  labs(x = "Publication Year", 
       y = "Mean OA Reported", 
       title = "Mean OA Reported + Range 'Error Bars'") +
  theme(legend.position = "none")
```

#### Study characteristics

-   table: description of information extracted from the included papers

-   total number papers

```{r}
length(unique(dat$AuthorYear))
```

-   distributions of features

```{r}
table(dat$AuthorYear ,dat$RS_devices)
```

```{r}
table(dat$research_theme)
```

```{r}
table(dat$model_group)
```

```{r}


```

-   maybe pair plot to show associations between features

#### **Meta-Analysis Results**:

-   pooled effect sizes and confidence intervals.

-   maybe with forest plots to visualize the individual study estimates (I have multiple results from one paper so maybe not the best method)

-   overall effect size

-   degree of heterogeneity

#### **Meta-Regression**

##### model results

-   results of the model, estimated coefficients, etc (table)

-   what features to add in the model

-   interpretation of results in the table

-   testing of assumptions (link to appendix?)

##### model fit

-   predictions vs observations

-   make table of the features and the predicted outcome (Klingwort&Toepoel)

::: {style="color: cornflowerblue"}
#### Reporting biases

-   funnel plots? TO DO: look at what is appropriate

#### Certainty of evidence
:::
