# Full text screening

Papers we all agreed on are subsetted as a starting point (maybe's and papers that are disagreed on will be reviewed at a later point)

First six papers were looked at to get an idea of the features that will be recorded. From this the following features will be looked for

+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| variable name                                                            | description                                                                                                                                                                   | example                          |
+==========================================================================+===============================================================================================================================================================================+==================================+
| performance measures: "R2, RMSE, MAPE, MNB, VP, recall, precision, ...." | numeric, one column per measure                                                                                                                                               |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| measure of interest group                                                |                                                                                                                                                                               | crop yeild, water quality, urban |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| measure of interest                                                      | target variable                                                                                                                                                               | Severe energy poverty index,     |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| RS_device                                                                | salalite , drone, plane, Unmanned Aerial Vehicles (UAVs)                                                                                                                      |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| RS_device_specifics                                                      | Sentinel-2, Landsat-8                                                                                                                                                         |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| type of sensors                                                          | hyperspectral, multispectral, and LiDAR                                                                                                                                       |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| type\_                                                                   | active vs optical                                                                                                                                                             |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| preprocessing                                                            | ....                                                                                                                                                                          |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| type of training/test set                                                | random sample of data,                                                                                                                                                        |                                  |
|                                                                          |                                                                                                                                                                               |                                  |
|                                                                          | temporal (forcasting),                                                                                                                                                        |                                  |
|                                                                          |                                                                                                                                                                               |                                  |
|                                                                          | spacial difference (training set a dif location to the test set)                                                                                                              |                                  |
|                                                                          |                                                                                                                                                                               |                                  |
|                                                                          | combination?                                                                                                                                                                  |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| model category                                                           | classification                                                                                                                                                                |                                  |
|                                                                          |                                                                                                                                                                               |                                  |
|                                                                          | regression                                                                                                                                                                    |                                  |
|                                                                          |                                                                                                                                                                               |                                  |
|                                                                          | segmentation                                                                                                                                                                  |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+
| model type                                                               | Unary Linear Regression (ULR), Multiple Linear Regression (MLR), Random Forest (RF), eXtreme Gradient Boosting (XGBoost), Support Vector Machine (SVM), Back Propagation (BP) |                                  |
+--------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------+

Because the first 6 papers are so different, the agreed papers are split into classification and regression

```{r eval=TRUE}
clas_v_reg <- read.csv("effort_clas_v_reg_nina.csv")
table(clas_v_reg$INCLUDE)
```

```{r}
df<- read.csv("10.1080:15481603.2022.2115589.csv")
library(tidyr)
df2<- gather(df, location, OA, IKONOS:WV.3)
write.csv(df2, "df2.csv")
```

```{r}
df<- subset(clas_v_reg, clas_v_reg$INCLUDE == "class")
doi <- df$DOI

x <- subset(citations, citations$DOI %in% doi)

my_data <- x[, c(11, 5:8)]
write.csv(my_data, "extracted.data.csv")

```
